Luminosity function and flux function\\ or\\ How far to the brightest beacon?

### 2015-12-15 luminosity.tex
example figures for flux distirbution within radius R (fig.2) are now corresponding to fig.1.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[htbp]
   \plotoneh{Prob_alpha10.pdf}
   \plotoneh{Prob_alpha30.pdf}
   \caption{Flux distribution of sources in a spherical shell at distance $r$ when $L_{\rm min}=1$ and $L_{\rm max}=10^6$.}
  \label{fig:prob}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Examples with $\alpha = 3.1$ and $\alpha = 1.5$ are shown in Figure \ref{fig:dndF}.
For demonstration, we consider $L_{\rm min } = 7\times 10^3~{\rm W/Hz}$, $L_{\rm max} = 1.5\times 10^6~{\rm W/Hz}$. 
The flux distribution from a sphere composes of three regimes: in the order of increasing flux, 1) zero flux, 2) a power law which depends on the luminosity function, and 3) a power law with index -2.5.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[htbp]
   \plotoneh{dndF_alpha31.pdf}
   \plotoneh{dndF_alpha15.pdf}
   \caption{Flux distribution of sources within radius $R$ with varying power-law index and $L_{\rm min } = 7\times 10^3~{\rm W/Hz}$, $L_{\rm max} = 1.5\times 10^6~{\rm W/Hz}$. The $y$-axis is arbitrary. }
  \label{fig:dndF}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

Examples with $\alpha = 1.0$ and $\alpha = 3.0$ are shown in Figure \ref{fig:prob}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[htbp]
   \plotoneh{Prob_alpha10.pdf}
   \plotoneh{Prob_alpha30.pdf}
   \caption{Flux distribution of sources in a spherical shell at distance $r$ when $L_{\rm min}=1$ and $L_{\rm max}=10^6$. Number density of the sources is assumed to be $10^{-3}~{\rm pc}^{-3}$.}
  \label{fig:prob}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Examples with $\alpha = 1.0$ and $\alpha = 3.0$ are shown in Figure \ref{fig:dndF}.
For demonstration, we consider $L_{\rm min } = 1$, $L_{\rm max} = 10^6$. 
The flux distribution from a sphere composes of three regimes: in the order of increasing flux, 1) zero flux, 2) a power law which depends on the luminosity function, and 3) a power law with index -2.5.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[htbp]
   \plotoneh{dN_dF_alpha1.pdf}
   \plotoneh{dN_dF_alpha3.pdf}
   \caption{Flux distribution of sources within radius $R$ with varying power-law index and $L_{\rm min } = 1$, $L_{\rm max} = 10^6$. Number density of the sources is assumed to be $10^{-3}~{\rm pc}^{-3}$.}
  \label{fig:dndF}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
